Erratum: Causal Compatibility Inequalities Admitting Quantum Violations in the Triangle Structure

### 2020-07-14 CCIAQVTS/CCIAQVTS_errata.tex
final edits to the errata

    One avenue for correcting the above inequality would be to simply reverse the direction of the inequality sign ($\leq \mapsto \geq$), or equivalently flip the sign of each of the coefficients. While the inequality resulting from such a correction would indeed be a valid causal compatibility inequality for the triangle structure, it has the undesirable feature of being \textit{satisfied} by the Fritz's distribution $P_{\text{F}}$ with a numerical value of $\frac{1}{16} \geq 0$.

@@

    It is also worth noting that the qualitative features of the wagon-wheel inequality discussed in the ``Numerical optimization results'' section of the published article were actually obtained from our proposed substitute inequality~(\ref{eq:ww_ineq_correct}), not the incorrectly published inequality~(\ref{eq:ww_ineq_incorrect}), and therefore those comments do not require any alteration. Inequality~(\ref{eq:ww_ineq_incorrect}) was published in place of inequality~(\ref{eq:ww_ineq_correct}) due to an error made by the first author during the final drafting stages of the manuscript.

@@

    % \bibliographystyle{apsrev4-1}
    \nocite{apsrev41Control}
    \bibliography{references}

>>>>

    One avenue for correcting the above inequality would be to simply reverse the direction of the inequality sign ($\leq \mapsto \geq$), or equivalently flip the sign of each of the coefficients. While the inequality resulting from such a correction would indeed be a valid causal compatibility inequality for the triangle structure, it has the undesirable feature of being \textit{satisfied} by Fritz's distribution $P_{\text{F}}$ with a numerical value of $\frac{1}{16} \geq 0$.

@@

    It is also worth noting that the qualitative features of the wagon-wheel inequality discussed in the ``Numerical optimization results'' section of the published article were actually determined using, and thus pertain to, our proposed substitute inequality~(\ref{eq:ww_ineq_correct}), not the incorrectly published inequality~(\ref{eq:ww_ineq_incorrect}). Consequently, those comments do not require any alteration. Inequality~(\ref{eq:ww_ineq_incorrect}) was published in place of inequality~(\ref{eq:ww_ineq_correct}) due to an error made by the first author during the final drafting stages of the manuscript.

@@

    % \bibliographystyle{apsrev4-1}
    %\nocite{apsrev41Control}
    %\bibliography{references}
